Optimized Synthesized Spectrum

### 2016-10-08 paper/ms.tex
Update ms.tex

\item[Structure]
There are four sections. The first part is the introduction part, which describes the background of the method. Then in the assumptions and method part, we show the detail of our method. The next section is the experiment, where the experiment results are showed. Finally, we discuss our results?
\end{description}
\end{abstract}

@@

popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0)
\bigskip

@@

parameters are a, b and c

The result is \(a+b+c = 0.982\). (a,b,c) = ()

@@

If the optimization works, we will optimized \(\theta_{j}\) besides a,b and c, which will come soon.

@@

%\includegraphics[width=70mm]{figure_1.png}

 Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
 chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 302.41 and 304.21
 They are similar to each other.

>>>>

\item[Structure]
There are four sections. The first part is the introduction part, which describes the background of the method. Then in the assumptions and method part, we show the detail of our method. The next section is the experiment, where the experiment results are showed. Finally, we discuss our results.
\end{description}
\end{abstract}

@@

popt, pcov= optimization.curve\_fit(func, (x\_data, y\_data, z\_data),nor\_r, x0, sigma=error)
\bigskip

@@

parameters are a, b and c. b should be much bigger than both a and c. And a+b+c should be equal to 1.

The result is \(a+b+c = 0.9996\).

(a,b,c) = (0.0423 ,0.9173 ,0.0404 ).

@@

If the optimization works, we will optimized \(\theta_{j}\) besides a, b and c, which will come soon.

@@

%\includegraphics[width=70mm]{figure_1.png}
%\includegraphics[width=70mm]{figure_2.png}

 Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
 chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are  9431.78 and 9360.95 .
 The optimized flux has a 1\% smaller chi-squared, which means our optimization works.
